Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
translating igor's explanation + adding comment

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}. \Mar{igor,
  nao consigo entender o porque deste caso nao dar aqueles erros
  (ReferenceError/TypeError) que vc. me mostrou e estourar na
  assercao. explique e de um exemplo concreto, por favor$\rightarrow$
}
\Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
diferente da que usamos anteriormente. Por exemplo, existem testes que 
estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
}
\textbf{Non-Standard Element.} This kind corresponds to the cases the
test case relies on some non-standard function or property of a
standard object. \Mar{igor, ha alguma explicacao/intuicao para
  explicar porque nao conseguir classificar
  isto?.$\rightarrow$}
  \Igor{Exemplos: Testes especificos do engenho que }
  \textbf{Unknown.} This category includes the
cases we were unable to confidently diagnose the failure but we
suspected it was a false alarm.

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{5}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
    & Timeout/OME & 28 & 13 \\
    & * Invalid Input & 39 & 48 \\    
    & * Error Message Mismatch & 41 & 12 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 34 & 28\\
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
%% \Mar{igor,
%%   nao consigo entender o porque deste caso nao dar aqueles erros
%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
%% }
%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
%% }
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
\Igor{Exemplos: Testes especificos do engenho que }\Mar{nao
  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
  seja mais especifico, por favor!}  \textbf{Unknown.} This category
includes the cases we were unable to confidently diagnose the failure
but we suspected it was a false alarm.

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    and true positives.}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{False Positives} & Undefined Behavior & 26 & 9 \\
    & Timeout/OME & 28 & 13 \\
    & * Invalid Input & 39 & 48 \\    
    & * Error Message Mismatch & 41 & 12 \\
    \midrule
    \multirow{2}{*}{True Positives} & Duplicate & 34 & 28\\
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}
